Adaptive broadcast tree for multicores

### 2013-06-06 paper.tex
Move to Laptop

\documentclass{article}
\usepackage{url,color,xspace,verbatim,subfig,ctable,multirow,listings}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}
\usepackage{rotating}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{graphics}
\usepackage{enumitem}
\usepackage{times}
\usepackage{amssymb}
\usepackage[colorlinks=true]{hyperref}
\usepackage[ruled,vlined]{algorithm2e}

% ==================================================

@@

@@

>>>>

\documentclass{article}
\usepackage{url,color,xspace,verbatim,subfig,ctable,multirow,listings}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}
\usepackage{rotating}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{graphics}
\usepackage{enumitem}
\usepackage{times}
\usepackage{amssymb}
\usepackage[colorlinks=true]{hyperref}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[toc,page]{appendix}
% ==================================================

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UMP performance}

Plot~\ref{pgfplot:20130605} shows the latency of UMP on ziger as the
number of cycles required for a RTT between core 0 and each of the
other cores.

\begin{figure}
  \caption{UMP latency between core 0 and target core}
  \label{pgfplot:20130605}
  \begin{tikzpicture}
    \begin{axis}[
        xlabel={target core},
        ylabel={cycles},
        ymin=0
        ]
    \addplot[
        color=red,
        mark=x,
        error bars/y dir=both,
        error bars/y explicit
        ] coordinates {
      (0,905.302469) +- (5.475974,5.475974)
      (1,899.453086) +- (4.273189,4.273189)
      (2,900.216049) +- (6.050119,6.050119)
      (3,908.808642) +- (6.189132,6.189132)
      (4,900.155556) +- (5.692577,5.692577)
      (5,1139.145679) +- (5.447710,5.447710)
      (6,1139.200000) +- (5.011050,5.011050)
      (7,1135.722222) +- (7.258244,7.258244)
      (8,1141.523457) +- (6.521385,6.521385)
      (9,1132.918519) +- (5.502482,5.502482)
      (10,1131.333333) +- (4.893432,4.893432)
      (11,1151.814815) +- (6.316764,6.316764)
      (12,1153.251852) +- (6.078156,6.078156)
      (13,1153.269136) +- (5.148574,5.148574)
      (14,1150.670370) +- (4.862935,4.862935)
      (15,1152.801235) +- (7.096426,7.096426)
      (16,1157.601235) +- (7.356042,7.356042)
      (17,1395.401235) +- (5.607601,5.607601)
      (18,1394.076543) +- (7.313209,7.313209)
      (19,1390.329630) +- (5.080219,5.080219)
      (20,1391.237037) +- (5.837986,5.837986)
      (21,1390.192593) +- (4.992087,4.992087)
      (22,1397.954321) +- (4.711073,4.711073)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

Plot~\ref{pgfplot:20130605_send} shows the send cost for sending a message
from each core to core 0. This cost is nearly independent from which
core sends the message.

\begin{figure}
  \caption{UMP send cost between core 0 and target core}
  \label{pgfplot:20130605_send}
  \begin{tikzpicture}
    \begin{axis}[
        xlabel={target core},
        ylabel={cycles},
        ymin=0
        ]
    \addplot[
        color=red,
        mark=x,
        error bars/y dir=both,
        error bars/y explicit
        ] coordinates {
      (0,244.197531) +- (4.324549,4.324549)
      (1,246.407407) +- (4.943577,4.943577)
      (2,245.567901) +- (2.985307,2.985307)
      (3,244.543210) +- (5.632905,5.632905)
      (4,243.530864) +- (4.237069,4.237069)
      (5,245.061728) +- (5.160021,5.160021)
      (6,245.901235) +- (2.386200,2.386200)
      (7,247.481481) +- (4.643092,4.643092)
      (8,245.901235) +- (3.723814,3.723814)
      (9,243.197531) +- (3.305139,3.305139)
      (10,246.530864) +- (2.277569,2.277569)
      (11,243.913580) +- (4.795053,4.795053)
      (12,246.259259) +- (3.640573,3.640573)
      (13,243.469136) +- (4.121867,4.121867)
      (14,242.283951) +- (3.732522,3.732522)
      (15,244.851852) +- (6.142568,6.142568)
      (16,242.209877) +- (4.302500,4.302500)
      (17,258.012346) +- (4.010769,4.010769)
      (18,256.765432) +- (4.266642,4.266642)
      (19,256.592593) +- (6.050768,6.050768)
      (20,255.382716) +- (4.226804,4.226804)
      (21,258.666667) +- (5.003702,5.003702)
      (22,255.567901) +- (4.219117,4.219117)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

Plot~\ref{pgfplot:20130605} shows the receive time on every core when
receiving a UMP message from core 0.

\begin{figure}
  \caption{UMP receive time between core 0 and target core}
  \label{pgfplot:20130605}
  \begin{tikzpicture}
    \begin{axis}[
        xlabel={target core},
        ylabel={cycles},
        ymin=0
        ]
    \addplot[
        color=red,
        mark=x,
        error bars/y dir=both,
        error bars/y explicit
        ] coordinates {
      (0,262.716049) +- (19.216913,19.216913)
      (1,250.864198) +- (18.156897,18.156897)
      (2,253.271605) +- (16.264794,16.264794)
      (3,264.481481) +- (19.195621,19.195621)
      (4,262.876543) +- (20.073558,20.073558)
      (5,406.592593) +- (12.717032,12.717032)
      (6,417.086420) +- (16.644576,16.644576)
      (7,414.913580) +- (19.692198,19.692198)
      (8,417.024691) +- (15.754267,15.754267)
      (9,416.345679) +- (20.657800,20.657800)
      (10,417.320988) +- (15.662984,15.662984)
      (11,432.172840) +- (28.319513,28.319513)
      (12,427.814815) +- (22.042110,22.042110)
      (13,429.234568) +- (26.883963,26.883963)
      (14,424.814815) +- (18.533994,18.533994)
      (15,426.283951) +- (17.456991,17.456991)
      (16,425.444444) +- (15.939701,15.939701)
      (17,506.333333) +- (9.086688,9.086688)
      (18,503.679012) +- (7.018190,7.018190)
      (19,518.222222) +- (9.838197,9.838197)
      (20,522.506173) +- (9.367824,9.367824)
      (21,517.111111) +- (9.108401,9.108401)
      (22,504.703704) +- (6.788597,6.788597)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

@@

\end{appendices}
